API design for machine learning software: experiences from the scikit-learn project

### 2013-09-27 paper.tex
tightly packed bibliography
some minor trimming

The \sklearn project provides a comprehensive suite of machine learning tools,
packaged as a library for the Python programming language.
It extends this general-purpose language with machine learning operations:
learning algorithms, preprocessing tools, model selection procedures
and a composition mechanism to produce complex ML workflows.
The ambition of the project is to provide efficient implementations
of well-established ML algorithms within a
programming environment that is accessible to non-experts and
reusable in various scientific areas.
The library is distributed under the simplified BSD license
to encourage its use in both academia and industry.

@@

{\small
\bibliographystyle{abbrvnat}
\DeclareRobustCommand{\VAN}[3]{#3}
\bibliography{paper}
}

>>>>

The \sklearn project provides a comprehensive suite of machine learning tools,
packaged as a Python library.
It extends this general-purpose language with machine learning operations:
learning algorithms, preprocessing tools, model selection procedures
and a composition mechanism to produce complex ML workflows.
The ambition of the project is to provide efficient implementations
of well-established algorithms within a
programming environment that is accessible to non-experts and
reusable in various scientific areas.
The library is distributed under the simplified BSD license
to encourage its use in both academia and industry.

@@

{\small
\bibliographystyle{abbrvnat}
\setlength{\bibsep}{1mm}
\DeclareRobustCommand{\VAN}[3]{#3}
\bibliography{paper}
}
